---
title: "New Allen MOUSE_Jan 20, 2020"
author: "Vivek Mahadevan"
date: "January 27, 2020"
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
    toc: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    fig.align='center',
    fig.pos='H',
    fig.path = "plots/",
    dev = c("svg"),
    dpi=500
)
```


#Allen MOUSE analyses
```{r}
library(tidyverse)
library(mclust)
library(stringi)
library(umap)
library(zoo)
library(dplyr)
library(Seurat)
library(ggplot2)
library(cowplot)
library(DT)
library(reticulate)
library(knitr)
library(rgl)

```
####### Reload datasets 
#######
#######
#######

```{r}
allen.mouse.seurat.object.cluster <- readRDS(file = "~/allen.mouse.seurat.object.cluster.rds")
```


#Rename the clusters based on known markers; ALLEN MOUSE
```{r VlnPlots, fig.height = 5, fig.width = 10, cache=TRUE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align='center',
  fig.pos='H',
  fig.path = "plots/",
  dev = c("svg"),
  dpi=500
)

rename.allen.mouse.clusters = RenameIdents(object = allen.mouse.seurat.object.cluster, 
                                           "1" = "Fibroblast", 
                                           "2" = "Microglia.1", 
                                           "3" = "GABA.MGE.SST.CHODL", 
                                           "4" = "GABA.CGE.VIP.CALB2", 
                                           "5" = "GABA.CGE.VIP.CRH", 
                                           "6" = "Astrocyte", 
                                           "7" = "Microglia.2", 
                                           "8" = "Endothelia",
                                           "9" = "Mural", 
                                           "10" = "Oligodendrocyte", 
                                           "11" = "GABA.CGE.NGFC", 
                                           "12" = "GABA.MGE.SST.RAB3B", 
                                           "13" = "GABA.MGE.SST.TH", 
                                           "14" = "GABA.CGE.VIP.CNR1", 
                                           "15" = "GABA.CGE.CALB2.CNR1", 
                                           "16" = "GABA.CGE.MEIS2",
                                           "17" = "GLUT.1.CX.L6", 
                                           "18" = "GLUT.2.CX.L6", 
                                           "19" = "GLUT.3.CX.L2/3", 
                                           "20" = "GLUT.4.HPC.Granule", 
                                           "21" = "GLUT.5.Sub", 
                                           "22" = "GLUT.6.HPC.CA1/2/3",
                                           "23" = "GLUT.7", 
                                           "24" = "GLUT.8", 
                                           "25" = "GLUT.9.CX.L5", 
                                           "26" = "GLUT.10", 
                                           "27" = "GLUT.11.CX.L4/5", 
                                           "28" = "GLUT.12.CX.L4/5", 
                                           "29" = "GLUT.13.CX.L4/5", 
                                           "30" = "GLUT.14.CX.L2/3", 
                                           "31" = "GLUT.15.CX.L6", 
                                           "32" = "GLUT.16.HPC.CA1/2/3",
                                           "33" = "GLUT.17.CX.L2/3", 
                                           "34" = "GLUT.18.CX.L6", 
                                           "35" = "GLUT.19.CX.L6", 
                                           "36" = "GABA.MGE.NGFC", 
                                           "37" = "GABA.MGE.PVALB.TAC1",
                                           "38" = "GABA.MGE.PVALB.PTHLH")



rename1.allen.mouse.clusters = RenameIdents(object = allen.mouse.seurat.object.cluster, 
                                            "1" = "Fibroblast", 
                                            "2" = "Microglia", 
                                            "3" = "GABA.MGE.SST", 
                                            "4" = "GABA.CGE.VIP", 
                                            "5" = "GABA.CGE.VIP", 
                                            "6" = "Astrocyte", 
                                            "7" = "Microglia", 
                                            "8" = "Endothelia",
                                            "9" = "Mural", 
                                            "10" = "Oligodendrocyte", 
                                            "11" = "GABA.CGE.NGFC", 
                                            "12" = "GABA.MGE.SST", 
                                            "13" = "GABA.MGE.SST", 
                                            "14" = "GABA.CGE.VIP", 
                                            "15" = "GABA.CGE.CALB2", 
                                            "16" = "GABA.CGE.MEIS2",
                                            "17" = "GLUT.CX", 
                                            "18" = "GLUT.CX", 
                                            "19" = "GLUT.CX", 
                                            "20" = "GLUT.HPC.Granule", 
                                            "21" = "GLUT.SUB", 
                                            "22" = "GLUT.HPC.CA1/2/3",
                                            "23" = "GLUT", 
                                            "24" = "GLUT", 
                                            "25" = "GLUT.CX", 
                                            "26" = "GLUT", 
                                            "27" = "GLUT.CX", 
                                            "28" = "GLUT.CX", 
                                            "29" = "GLUT.CX", 
                                            "30" = "GLUT.CX", 
                                            "31" = "GLUT.CX", 
                                            "32" = "GLUT.HPC.CA1/2/3",
                                            "33" = "GLUT.CX", 
                                            "34" = "GLUT.CX", 
                                            "35" = "GLUT.CX", 
                                            "36" = "GABA.MGE.NGFC", 
                                            "37" = "GABA.MGE.PVALB",
                                            "38" = "GABA.MGE.PVALB")



rename2.allen.mouse.clusters = RenameIdents(object = allen.mouse.seurat.object.cluster, 
                                            "1" = "Non-neurons", 
                                            "2" = "Non-neurons", 
                                            "3" = "GABA.MGE", 
                                            "4" = "GABA.CGE", 
                                            "5" = "GABA.CGE", 
                                            "6" = "Non-neurons", 
                                            "7" = "Non-neurons", 
                                            "8" = "Non-neurons",
                                            "9" = "Non-neurons", 
                                            "10" = "Non-neurons", 
                                            "11" = "GABA.CGE", 
                                            "12" = "GABA.MGE", 
                                            "13" = "GABA.MGE", 
                                            "14" = "GABA.CGE", 
                                            "15" = "GABA.CGE", 
                                            "16" = "GABA.CGE",
                                            "17" = "GLUT", 
                                            "18" = "GLUT", 
                                            "19" = "GLUT", 
                                            "20" = "GLUT", 
                                            "21" = "GLUT", 
                                            "22" = "GLUT",
                                            "23" = "GLUT", 
                                            "24" = "GLUT", 
                                            "25" = "GLUT", 
                                            "26" = "GLUT", 
                                            "27" = "GLUT", 
                                            "28" = "GLUT", 
                                            "29" = "GLUT", 
                                            "30" = "GLUT", 
                                            "31" = "GLUT", 
                                            "32" = "GLUT",
                                            "33" = "GLUT", 
                                            "34" = "GLUT", 
                                            "35" = "GLUT", 
                                            "36" = "GABA.MGE", 
                                            "37" = "GABA.MGE",
                                            "38" = "GABA.MGE")



marker.genes <- list(set1 = c("Mt2", "Olig1", "C1qa", "Cldn5", "Vtn", "Snap25", "Slc17a7", "Gad1", "Dcx"),
                     set2 = c("Nkx2-1", "Lhx6", "Gad1", "Gad2", "Slc32a1", "Slc6a1", "Lamp5", "Sst", "Pvalb"),
                     set3 = c("Lamp5", "Id2", "Reln", "Npy", "Nos1", "Cacna2d1", "Ndnf", "Hapln1", "Cck"),
                     set4 = c("Lamp5", "Ndnf", "Plch2", "Dock5", "Ntn1", "Npy2r", "Fam19a1", "Tmem182", "Pax6"),
                     set5 = c("Sst", "Elfn1", "Chodl", "Reln", "Nos1", "Pvalb", "Pthlh", "Erbb4", "Tac1"),
                     set6 = c("Prox1", "Htr3a", "Vip", "Cnr1", "Sp8", "Sp9", "Dcx", "Htr3b", "Nr2f2"),
                     set7 = c("Kcna1", "Kcna2", "Kcna6", "Kcnd2", "Kcnd3", "Kcns3", "Kcnh1", "Kcnq5", "Kcnc4"),
                     set8 = c("Kcna6", "Kcnc2", "Kcnh7", "Kcnc4", "Kcns3", "Kcnq3", "Cacna1a", "Cacna1b", "Cacna1e"),
                     set9 = c("Kcnip1", "Kcnip2", "Kcnip3", "Kcnip4", "Kcnb1", "Dpp6", "Dpp10", "Pin1"))

```


#Non-linear dimensional reduction (using UMAP) without labels
#The following plots show the UMAP dimensional reduction with each cluster colored and labeled.

```{r tSNE1, results='asis', fig.height = 5, fig.width = 10, cache=TRUE}
DimPlot(object = allen.mouse.seurat.object.cluster, reduction = 'umap', label=FALSE)

DimPlot(object = rename.allen.mouse.clusters, reduction = 'umap', label=FALSE)

DimPlot(object = allen.mouse.seurat.object.cluster, reduction = 'umap', repel=TRUE, label=TRUE)

DimPlot(object = rename.allen.mouse.clusters, reduction = 'umap', repel=TRUE, label=TRUE)

```

#Non-linear dimensional reduction (using UMAP) without labels; AFTER RENAMING CLUSTERS
#The following plots show the UMAP dimensional reduction with each cluster colored and labeled.
```{r tSNE2, fig.height=5, fig.width=8, cache=TRUE, paged.print=TRUE, results='asis'}
dir.create('allen.mouse.figures', showWarnings=FALSE)

DimPlot(object = rename1.allen.mouse.clusters, reduction = 'umap', label=FALSE)

DimPlot(object = rename1.allen.mouse.clusters, reduction = 'umap', repel=TRUE, label=TRUE)

DimPlot(object = rename2.allen.mouse.clusters, reduction = 'umap', label=FALSE)

DimPlot(object = rename2.allen.mouse.clusters, reduction = 'umap', repel=TRUE, label=TRUE)


```

#Plot the Violin plots of control genes and Ram's test genes only across Neurons (GLUT/GABA.MGE/GABA.CGE)
```{r Vln Plots, fig.height = 2.5, fig.width = 6, cache=TRUE}
marker.genes.RAM.1 <- list(set1 = c("Slc17a7", "Gad1"),
                           set2 = c("Nkx2-1", "Lhx6", "Gad1", "Gad2", "Slc32a1", "Slc6a1", "Lamp5", "Sst", "Pvalb"),
                           set3 = c("Lamp5", "Id2", "Reln", "Npy", "Nos1", "Cacna2d1", "Ndnf", "Hapln1", "Cck"),
                           set4 = c("Lamp5", "Ndnf", "Plch2", "Dock5", "Ntn1", "Npy2r", "Fam19a1", "Tmem182", "Pax6"),
                           set5 = c("Sst", "Elfn1", "Chodl", "Reln", "Nos1", "Pvalb", "Pthlh", "Erbb4", "Tac1"),
                           set6 = c("Prox1", "Htr3a", "Vip", "Cnr1", "Sp8", "Sp9", "Dcx", "Htr3b", "Nr2f2"))

marker.genes.RAM.2 <- list(set1 = c("Kcna1", "Kcnab1", "Kcna2", "Kcna4", "Kcnc3", "Kcnc4",  "Kcnd1", "Kcnd2", "Kcnd3"),
                           set2 = c("Kcnip1", "Kcnip2", "Kcnip3", "Kcnip4", "Dpp6", "Dpp10"))

marker.genes.RAM.3 <- list(set1 = c("Kcna4", "Kcnc3", "Kcnc4", "Kcnd2", "Kcnd3"),
                           set2 = c("Kcna1", "Kcnab1"),
                           set3 = c("Kcnip1", "Kcnip2", "Kcnip3", "Kcnip4", "Dpp6", "Dpp10"),
                           set4 = c("Dpp6", "Dpp10"))


```


#Plot the Violin plots of control genes and Ram's test genes only across Neurons (GLUT/GABA.MGE/GABA.CGE)
```{r Vln Plots1, fig.height = 5, fig.width = 8, cache=TRUE}
for(name in names(marker.genes.RAM.1)){
  cat('\n### ', name, ' {.tabset}\n')
  for(feature in marker.genes.RAM.1[[name]]){
    cat('\n#### ', feature, '\n')
    print(VlnPlot(object = rename1.allen.mouse.clusters, assay='RNA', features=feature, 
                  idents = c(
                    "GLUT.HPC.CA1/2/3",
                    "GLUT.HPC.Granule", 
                    "GABA.MGE.PVALB",
                    "GABA.MGE.SST", 
                    "GABA.CGE.VIP", 
                    "GABA.CGE.CALB2", 
                    "GABA.CGE.NGFC", 
                    "GABA.MGE.NGFC"),
                  
                  pt.size=0.1, log=FALSE))
    cat('\n')
  }
}
```

```{r Vln Plots1, fig.height = 5, fig.width = 8, cache=TRUE}
for(name in names(marker.genes.RAM.2)){
  cat('\n### ', name, ' {.tabset}\n')
  for(feature in marker.genes.RAM.2[[name]]){
    cat('\n#### ', feature, '\n')
    print(VlnPlot(object = rename1.allen.mouse.clusters, assay='RNA', features=feature, 
                  idents = c(
                    "GLUT.HPC.CA1/2/3",
                    "GLUT.HPC.Granule", 
                    "GABA.MGE.PVALB",
                    "GABA.MGE.SST", 
                    "GABA.CGE.VIP", 
                    "GABA.CGE.CALB2", 
                    "GABA.CGE.NGFC", 
                    "GABA.MGE.NGFC"),
                  
                  y.max= 4, pt.size=0, log=FALSE))
    cat('\n')
  }
}
```


#Feature plots of control genes and Ram's test genes
```{r Feature Plots2, fig.height = 15, fig.width = 15, cache=TRUE}
for(name in names(marker.genes.RAM.1)){
  cat('\n### ', name, '  \n')
  print(FeaturePlot(rename1.allen.mouse.clusters, features = marker.genes.RAM.1[[name]], min.cutoff = "q9"))
  cat('\n')
}

for(name in names(marker.genes.RAM.2)){
  cat('\n### ', name, '  \n')
  print(FeaturePlot(rename1.allen.mouse.clusters, features = marker.genes.RAM.2[[name]], min.cutoff = "q9"))
  cat('\n')
}

```

```{r Vln Plots1, fig.height = 5, fig.width = 8, cache=TRUE}
for(name in names(marker.genes.RAM.2)){
  cat('\n### ', name, ' {.tabset}\n')
  for(feature in marker.genes.RAM.2[[name]]){
    cat('\n#### ', feature, '\n')
    print(VlnPlot(object = rename1.allen.mouse.clusters, assay='RNA', features=feature, 
                  idents = c(
                    "GLUT.HPC.CA1/2/3",
                    "GLUT.HPC.Granule", 
                    "GABA.MGE.PVALB",
                    "GABA.MGE.SST", 
                    "GABA.CGE.VIP", 
                    "GABA.CGE.CALB2", 
                    "GABA.CGE.NGFC", 
                    "GABA.MGE.NGFC"),
                  
                  y.max= 4, pt.size=0.1, log=FALSE, single.legend=TRUE, size.x.use=0))
    cat('\n')
  }
}
```

#Raw expressions of KCN genes from all clusters
```{r Vln Plots1, fig.height = 5, fig.width = 8, cache=TRUE}

as.matrix(rename1.allen.mouse.clusters@assays$RNA@data[c("Kcna1", "Kcnab1", "Kcna2", "Kcna4", "Kcnc3", "Kcnc4", "Kcnd1", "Kcnd2", "Kcnd3", "Kcnip1", "Kcnip2", "Kcnip3", "Kcnip4", "Dpp6", "Dpp10"), ] )
KCN.matrix.all <-t(as.matrix(rename1.allen.mouse.clusters@assays$RNA@data[c("Kcna1", "Kcnab1", "Kcna2", "Kcna4", "Kcnc3", "Kcnc4", "Kcnd1", "Kcnd2", "Kcnd3", "Kcnip1", "Kcnip2", "Kcnip3", "Kcnip4", "Dpp6", "Dpp10"), ] ))
KCN.matrix.all[1:38,]
head(rename1.allen.mouse.clusters@active.ident) 
head(rename1.allen.mouse.clusters@meta.data)  

KCN.celltype = rename1.allen.mouse.clusters@meta.data$tree.ident
KCN = cbind(KCN.matrix.all,KCN.celltype)
class(KCN)
KCN[1:38,]
write.table(x = KCN, file = "~/Mouse.KCN.expression.tsv",quote = FALSE, sep = "\t", col.names = TRUE, row.names=FALSE)
```

ggplot2::qplot(Kcnd2, Kcnd3, data = as.data.frame(KCN), colour = as.factor(KCN.celltype))
```

#Raw expressions of Control genes from all clusters
```{r Raw expressions, fig.height = 5, fig.width = 8, cache=TRUE}


as.matrix(rename1.allen.mouse.clusters@assays$RNA@data[c("Gad1", "Gad2", "Lhx6", "Pvalb", "Pthlh", "Sst", "Chodl", "Lamp5", "Hapln1", "Id2", "Reln", "Ndnf", "Prox1", "Htr3a", "Vip", "Calb2", "Slc17a7", "Dgkg", "St6galnac5", "Cpne7", "Ncdn", "C1ql2"), ] )
GABA.GlUT.Control.matrix.all <-t(as.matrix(rename1.allen.mouse.clusters@assays$RNA@data[c("Gad1", "Gad2", "Lhx6", "Pvalb", "Pthlh", "Sst", "Chodl", "Lamp5", "Hapln1", "Id2", "Reln", "Ndnf", "Prox1", "Htr3a", "Vip", "Calb2", "Slc17a7", "Dgkg", "St6galnac5", "Cpne7", "Ncdn", "C1ql2"), ] ))
GABA.GlUT.Control.matrix.all[1:38,]
head(rename1.allen.mouse.clusters@active.ident)  
head(rename1.allen.mouse.clusters@meta.data) 

GABA.GlUT.Control.celltype = rename1.allen.mouse.clusters@meta.data$tree.ident
GABA.GlUT.Control = cbind(GABA.GlUT.Control.matrix.all,GABA.GlUT.Control.celltype)
class(GABA.GlUT.Control)
GABA.GlUT.Control[1:38,]
write.table(x = GABA.GlUT.Control, file = "~/Mouse.GABA.GlUT.Control.expression.tsv",quote = FALSE, sep = "\t", col.names = TRUE, row.names=FALSE)
```
