---
title: "New Allen Mouse and Human_Jan 20, 2020"
author: "Vivek Mahadevan"
date: "January 20, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    fig.align='center',
    fig.pos='H',
    fig.path = "plots/",
    dev = c("svg"),
    dpi=500
)
```


#Allen MOUSE analyses
```{r}
library(tidyverse)
library(mclust)
library(stringi)
library(umap)
library(zoo)
library(dplyr)
library(Seurat)
library(ggplot2)
library(cowplot)
library(DT)
library(reticulate)
library(knitr)
library(rgl)

data_dir <- "~/allen-brain-map/mouse/"
list.files(data_dir) 
allen.mouse <- Read10X((data.dir = data_dir), gene.column=1)
allen.mouse.seurat.object = CreateSeuratObject(counts = allen.mouse, min.cells = 3, min.features = 200, project = "10X_allen.mouse")
allen.mouse.seurat.object

allen.mouse.seurat.object[["percent.mt"]] <- PercentageFeatureSet(allen.mouse.seurat.object, pattern = "^MT-")
VlnPlot(allen.mouse.seurat.object, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
plot1 <- FeatureScatter(allen.mouse.seurat.object, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(allen.mouse.seurat.object, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
CombinePlots(plots = list(plot1, plot2))
allen.mouse.seurat.object <- subset(allen.mouse.seurat.object, subset = nFeature_RNA > 200 & nFeature_RNA < 20000 & percent.mt < 5)


allen.mouse.seurat.object <- NormalizeData(allen.mouse.seurat.object, normalization.method = "LogNormalize", scale.factor = 10000)
allen.mouse.seurat.object <- NormalizeData(allen.mouse.seurat.object)


allen.mouse.seurat.object <- FindVariableFeatures(allen.mouse.seurat.object, selection.method = "vst", nfeatures = 2000)
top10 <- head(VariableFeatures(allen.mouse.seurat.object), 10)
plot1 <- VariableFeaturePlot(allen.mouse.seurat.object)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
CombinePlots(plots = list(plot1, plot2))

all.genes <- rownames(allen.mouse.seurat.object)
allen.mouse.seurat.object <- ScaleData(allen.mouse.seurat.object, features = all.genes)

allen.mouse.seurat.object <- RunPCA(allen.mouse.seurat.object, features = VariableFeatures(object = allen.mouse.seurat.object))
print(allen.mouse.seurat.object[["pca"]], dims = 1:5, nfeatures = 5)
VizDimLoadings(allen.mouse.seurat.object, dims = 1:2, reduction = "pca")
DimPlot(allen.mouse.seurat.object, reduction = "pca")
DimHeatmap(allen.mouse.seurat.object, dims = 1, cells = 500, balanced = TRUE)
DimHeatmap(allen.mouse.seurat.object, dims = 1:15, cells = 500, balanced = TRUE)


allen.mouse.seurat.object <- JackStraw(allen.mouse.seurat.object, num.replicate = 100)
allen.mouse.seurat.object <- ScoreJackStraw(allen.mouse.seurat.object, dims = 1:20)
JackStrawPlot(allen.mouse.seurat.object, dims = 1:20)
ElbowPlot(object = allen.mouse.seurat.object, ndims = 40, reduction = "pca")


allen.mouse.seurat.object <- FindNeighbors(allen.mouse.seurat.object, dims = 1:40)
allen.mouse.seurat.object <- FindClusters(allen.mouse.seurat.object, resolution = 0.6)
head(Idents(allen.mouse.seurat.object), 5)

```
#allen.mouse.seurat.object
#BuildClusterTree
```{r cluster tree, cache=TRUE}


allen.mouse.seurat.object.cluster = BuildClusterTree (object = allen.mouse.seurat.object, reorder = TRUE, reorder.numeric = TRUE)
PlotClusterTree(allen.mouse.seurat.object.cluster)
```

#Non-linear dimensional reduction (using UMAP)
#The following plots show the UMAP dimensional reduction with each cluster colored and labeled.
```{r tSNE1, results='asis', fig.height = 5, fig.width = 10, cache=TRUE}

allen.mouse.seurat.object <- RunUMAP(object = allen.mouse.seurat.object, dims = 1:40)
DimPlot(object = allen.mouse.seurat.object, reduction = 'umap', label=TRUE)
DimPlot(object = allen.mouse.seurat.object, reduction = 'umap', label=FALSE)


allen.mouse.seurat.object.cluster <- RunUMAP(object = allen.mouse.seurat.object.cluster, dims = 1:40)
DimPlot(object = allen.mouse.seurat.object.cluster, reduction = 'umap', label=TRUE)
DimPlot(object = allen.mouse.seurat.object.cluster, reduction = 'umap', label=FALSE)

```
#Non-linear dimensional reduction (using UMAP) without labels
#The following plots show the UMAP dimensional reduction with each cluster colored and labeled.
```{r tSNE1, results='asis', fig.height = 5, fig.width = 10, cache=TRUE}

DimPlot(object = allen.mouse.seurat.object.cluster, reduction = 'umap', label=FALSE)

DimPlot(object = rename.allen.mouse.clusters, reduction = 'umap', label=FALSE)

DimPlot(object = allen.mouse.seurat.object.cluster, reduction = 'umap', repel=TRUE, label=TRUE)

DimPlot(object = rename.allen.mouse.clusters, reduction = 'umap', repel=TRUE, label=TRUE)


```
#Non-linear dimensional reduction (using UMAP) without labels; AFTER RENAMING CLUSTERS
#The following plots show the UMAP dimensional reduction with each cluster colored and labeled.
```{r tSNE1, fig.height=5, fig.width=8, cache=TRUE, paged.print=TRUE, results='asis'}

dir.create('allen.mouse.figures', showWarnings=FALSE)

DimPlot(object = rename1.allen.mouse.clusters, reduction = 'umap', label=FALSE)

DimPlot(object = rename1.allen.mouse.clusters, reduction = 'umap', repel=TRUE, label=TRUE)

DimPlot(object = rename2.allen.mouse.clusters, reduction = 'umap', label=FALSE)

DimPlot(object = rename2.allen.mouse.clusters, reduction = 'umap', repel=TRUE, label=TRUE)

```


#Number of cells per cluster actoss datasets
```{r cluster cell number, cache=TRUE}

table(Idents(allen.mouse.seurat.object.cluster))

```

#Save RDS file
```{r save_rds, cache=TRUE}
dir.create('output', showWarnings=FALSE)
saveRDS(allen.mouse.seurat.object.cluster, file = "output/allen.mouse.seurat.object.cluster.rds")
```
#Findallmarkers, mouse allen, DoHeatmap
```{r}
allen.mouse.all.markers <- FindAllMarkers(object = allen.mouse.seurat.object.cluster, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
head(x = allen.mouse.all.markers)
write.csv(x = allen.mouse.all.markers, file = "output/allen.mouse.all.markers.csv")
```

#DoHeatmap
```{r DoHeatmap, results='asis', fig.height = 10, fig.width = 20, cache=TRUE}
allen.mouse.all.markers %>% group_by(cluster) %>% top_n(n = 2, wt = avg_logFC)
top10 <- allen.mouse.all.markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_logFC)
DoHeatmap(allen.mouse.seurat.object.cluster, features = top10$gene)

```

